Generate data for NOBA cod ensemble modeling

### 2020-05-22 NOBAcod.Rmd
testing fishery catch at age (annual)

if(select_variable %in% c("Catch", "Discard")){
    #read in fleet names
    fleetnames <- load_fisheries(dir = dir, file_fish = file_fish)
    for(i in select_variable){
      sv <-paste0(i, "_", fleetnames$Code)
      sv1 <- c()
    }
  }

@@

>>>>

if(select_variable %in% c("Catch", "Discard")){
    #read in fleet names
    fleetnames <- load_fisheries(dir = dir, file_fish = file_fish)
    svfish <- c()
    for(i in select_variable){
      sv <-paste0(i, "_", fleetnames$Code)
      svfish <- c(svfish, sv)
    }
    select_variable <- svfish
  }

@@

Test new `load_nc_annage`:

```{r testfishery}

source(here("R/load_nc_annage.R"))
source(here("R/load_fisheries.R"))

fgs <- NOBAom$funct.groups
biolprm <- NOBAom$biol
select_groups <- c('Mackerel', 'North_atl_cod', 'Capelin')

file_nc <- "outputnordic_runresults_01ANNAGECATCH.nc"
file_fish <- "NoBAFisheries.csv"

fishcatchage <- load_nc_annage(dir = d.name,
                  file_nc = file_nc,
                  file_fish = file_fish,
                  bps = bps,
                  fgs = fgs,
                  biolprm = biolprm,
                  select_groups = select_groups,
                  select_variable = "Catch",
                  check_acronyms = TRUE,
                  bboxes = boxes, 
                  verbose = TRUE)

fishcatchage

fishdiscage <- load_nc_annage(dir = d.name,
                  file_nc = file_nc,
                  file_fish = file_fish,
                  bps = bps,
                  fgs = fgs,
                  biolprm = biolprm,
                  select_groups = select_groups,
                  select_variable = "Discard",
                  check_acronyms = TRUE,
                  bboxes = boxes, 
                  verbose = TRUE)

fishdiscage
```

Do we want catch by fishery? No fishery column here, check what it is doing.
